True versus apparent shapes of bow shocks

### 2018-02-26 papers/Papers1234/sec-conclusions.tex
Expand figure caption for 000-400 fits

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/new-000-400-multi-fig}
  \caption{Example empirical determination of planitude and alatude
    for an observed bow shock.  An \textit{HST} H\(\alpha\) image (ACS
    F658N filter) of M42~000-400 is shown in color scale and contours
    \citep{Bally:2006a}.}
  \label{fig:000-400-fit}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/new-000-400-multi-fig}
  \caption{Example empirical determination of planitude and alatude
    for an observed bow shock.  Color scale and contours show an
    \textit{HST} H\(\alpha\) image (ACS F658N filter,
    \citealp{Bally:2006a}) of M42~000-400. Three different bows have
    been traced by hand on the image (red and white filled symbols):
    (\textit{a})~outer edge, (\textit{b})~ridge of maximum emission,
    and (\textit{c})~inner edge.  For each panel, the dark-colored
    circle shows the initial fit to the full set of points (white and
    red), using the algorithm described in
    Appendix~\ref{app:rcurv-empirical}.  The center of curvature and
    derived axis are shown by a small filled circle and dashed line in
    the same color. Lighter colored circles show three subsequent
    iterations where the fit is restricted to points within
    \(\pm\ang{75}\) of the axis.  The subset of points used in the
    final iteration is marked in red.  In panels \textit{b} and
    \textit{c} the iterations converge immediately, but in panel
    \textit{a} the iterations stably oscillate between two slightly
    different solutions.  (\textit{d})~Location of the converged
    circle fits in the projected planitude--alatude plane.  Each
    solution has two values of the alatude \(\Lambda'\), corresponding to
    \(R_{90}^+\) and \(R_{90}^-\).}
  \label{fig:000-400-fit}
\end{figure*}
